### 2017-02-02 paper1.tex
Add files via upload

Although most thermal remote sensors operate within one of the \gls{atmwind}[s] --- where atmospheric effects are greatly reduced --- virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared \gls{waveband} the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal almost certainly not equal to the ground emitted signal. For an isothermal, homogeneous surface-atmosphere system, at-sensor spectral radiance at height ($z$) can be described by a function deviating from a Planck curve at T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation governed by the difference between Planck curves at T\textsubscript{surf} and the ambient T\textsubscript{air}. As shown for two path geometries in \ref{spectairtsurf} for an atmosphere with water vapor content of  12 g/m\textsuperscript{3} and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere, an at-sensor spectral radiance signal deviates significantly from the surface emitted spectral radiance curve. A less transmissive atmosphere increases the potential for deviation in the at-sensor signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence on the spectral TIR signal.

\begin{figure}[!ht]
	\includegraphics[width=\textwidth]{spectairtsurf}
	\caption{At-sensor spectral directional radiances computed in MODTRAN 4.1 \cite{Berk1987} for short (30m) and long (3000m) path lengths (z) with Planck curves indicating spectral radiances at T\textsubscript{air} = 305 K and T\textsubscript{surf} = 295 K.}
	\label{spectairtsurf}
\end{figure}

Atmospheric effects can lead to differences between the 'true' radiometric T\textsubscript{surf} and the remote sensed T\textsubscript{surf} of over 10 k for satellite platforms \cite{Cooper1989} and over 6 K for near-ground sensors \cite{Meier2011}. Moreover, because atmospheric and emissivity effects are a function of non-uniform and spatiotemporally variant surface and atmospheric properties, their associated errors change depending on instrument type, surface-sensor geometry, study location, and ambient conditions. As intersite and time-sequential analysis is a significant goal of most thermal remote sensed studies (urban or otherwise) these effects cannot be ignored.

Spectral transmission of longwave radiation through a given layer of atmosphere is dependent on total column absorber content (the principal broadband TIR absorbers are H\textsubscript{2}0, C0\textsubscript{2}, and to a lesser extent 0\textsubscript{3}, N\textsubscript{2}0, CO, CH\textsubscript{4}, and 0\textsubscript{2} \cite{Miskolczi1993}). Holding vertical absorber content constant, variation in band-by-band TIR transmittance with path length is greatest at urban scales (approximately 1 to 50 meters), where transparent spectral bands can quickly become opaque with small changes in path length or absorber content - illustrated in figure \ref{spectransheight}. Thus, transmittance of TIR near the surface is highly dependent on surface-sensor geometry, instrument spectral response, and atmospheric absorber content. Indeed, accurate assessment of atmospheric influence on TIR may be most complex when measured near the surface.

@@

\noindent where $ \sigma $ is the Stefan-Boltzmann constant and $ \overline{r} $ is Planck weighted average broadband sensor response computed as,

@@

In addition, a simple approximation of $T_{bright}$ can be inferred from directional radiance using equation \ref{stefb1} by replacing $ L_z $ with $L'_z$ multiplied by a constant. This method is commonly used to infer T\textsubscript{bright} from infrared thermometers (IRT) operating over the atmospheric window (where atmospheric correction magnitudes are small and T\textsubscript{bright} is a reasonably accurate approximation of T\textsubscript{surf}). However, constants must be calibrated for the range of expected T\textsubscript{surf} as the relationship between $ L_z $ and $L'_z$  is not perfectly linear.

Inversions of uncorrected directional radiances or irradiances using the Planck function or the Stefan-Boltzmann law yield a temperature equal to that of a blackbody emitting the same amount of radiation as detected by the sensor. Since $ L_z $ is unlikely to be equal to $ L_0 $, T\textsubscript{bright, 0} and T\textsubscript{bright, z} often show significant variation based on sensor characteristics, ambient conditions, and surface-sensor geometry. Hence, remote sensed T\textsubscript{bright} is generally considered only a rough approximation representation of kinetic or thermodynamic T\textsubscript{surf}.

To retrieve a more accurate estimation of the 'true' T\textsubscript{surf}, the same inversions can be applied to TIR measurements after correction for atmospheric and surface emissivity effects (e.g. transformations of the TIR signal to represent that at $ z = 0 $ if the surface was emitting as a perfect blackbody) to yield a direction radiometric surface temperature T\textsubscript{rad} for atmospheric and emissivity corrected directional radiances, a hemispherical radiometric surface temperature T\textsubscript{hem} for atmospheric and emissivity corrected irradiances. $ T\textsubscript{rad} (\theta, \phi) $ and T\textsubscript{hem} provide a better approximation of the ‘true’ T\textsubscript{surf} by representing the temperature at which the surface is radiating integrated over the sensor FOV.

@@

To calculate surface-sensor geometries, the Surface-Sensor-Sun Urban Model (SUM) \cite{Soux2004} is initialized with a simplified, orthogonal 3-dimensional DBM representing the street canyons and courtyards immediately surrounding the sensor. SUM uses a four-dimensional array to represent surface morphology   with three spatial dimensions ($x$, $y$, and $z$), with $z$ representing height above the $x$, $y$ plane. SUM also includes an additional fourth dimension, where properties describing each cell are stored (in this case, distance from the point to the sensor). After specifying sensor FOV and position relative to the DBM, the model determines which patches have an unobstructed line of sight to the sensor and calculates the distance from "seen" patches to the sensor. Path lengths are binned at 5$^{\circ}$ increments of zenith angle and averaged to return an azimuthally-independent mean path length for each bin. In addition, while simulating path length geometries, SUM calculates view factors for each solid angle "slice", which are later used to weight 2-dimensional angular radiances in the hemispherical integration post-processing steps.

\begin{figure}[!ht]
	\includegraphics[width=\textwidth]{23radtran}
	\label{23radtran}
	\caption{A typical 2-dimensional (b) radiative transfer schematic adapted for an idealized 3-dimensional urban area (a). In 3-dimensions, path length for a given zenith angle can change significantly with azimuth angle. Dotted lines indicate the potential for absorption by the intervening atmospheric layer}
\end{figure}

\subsection{Modeling hemispherical irradiances}
With path length geometries calculated in SUM, irradiances are modeled time-sequentially using the MODerate resolution atmospheric TRANsmission 4.1 radiative transfer code (MODTRAN) \cite{Berk1987}. At each time-step, a range of potential T\textsubscript{hem} is selected using T\textsubscript{bright} subtracted by some constant (6 K during nighttime runs and 4 K for daytime runs). In MODTRAN, at-sensor spectral radiances for each path length are modeled over a waveband of 0---2500cm\textsuperscript{-1} at 0.5 K intervals over the range of potential T\textsubscript{hem}. Atmospheric profiles are constructed from 30-minute averages of T\textsubscript{air} and humidity with aerosol and above-sensor conditions are informed by the mid-latitude summer standard atmosphere when daytime maximum T\textsubscript{air} is greater than 10 $^{\circ}$C (the mid-latitude winter profile is substituted on days with T\textsubscript{air, max} of less than 10 $^{\circ}$C). 
Spectral radiances are convolved by a dome transmittance.

\section{Evaluation of the method using profiles of upwelling longwave radiation over a homogenous planar surface}

>>>>

Although most thermal remote sensors operate within one of the \gls{atmwind}[s] --- where atmospheric effects are greatly reduced --- virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared \gls{waveband} the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal almost certainly not equal to the ground emitted signal. For an isothermal, homogeneous surface-atmosphere system, at-sensor spectral radiance at height ($z$) can be described by a function deviating from a Planck curve at T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation governed by the difference between Planck curves at T\textsubscript{surf} and the ambient T\textsubscript{air}. As shown for two path geometries in figure \ref{spectairtsurf} for an isothermal atmosphere with water vapor content of 12 \si{\gram\per\meter\cubed} and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere, an at-sensor spectral radiance signal deviates significantly from the surface emitted spectral radiance curve. A less transmissive atmosphere increases the potential for deviation in the at-sensor signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence on the spectral TIR signal.

\begin{figure}[!ht]
	\includegraphics[width=\textwidth]{spectairtsurf}
	\caption{At-sensor spectral directional radiances computed in MODTRAN 4.1 \cite{Berk1987} for short (30 \si{m}) and long (3000 \si{m}) path lengths (z) with Planck curves indicating spectral radiances at T\textsubscript{air} = 305 \si{K} and T\textsubscript{surf} = 295 \si{K}.}
	\label{spectairtsurf}
\end{figure}

Atmospheric effects can lead to differences between the 'true' radiometric T\textsubscript{surf} and the remote sensed T\textsubscript{surf} of over 10 \si{K} for satellite platforms \cite{Cooper1989} and over 6 \si{K} for near-ground sensors \cite{Meier2011}. Moreover, because atmospheric and emissivity effects are a function of non-uniform and spatiotemporally variant surface and atmospheric properties, their associated errors change depending on instrument type, surface-sensor geometry, study location, and ambient conditions. As intersite and time-sequential analysis is a significant goal of most thermal remote sensed studies (urban or otherwise) these effects cannot be ignored.

Spectral transmission of longwave radiation through a given layer of atmosphere is dependent on total column absorber content (the principal broadband TIR absorbers are H\textsubscript{2}0, C0\textsubscript{2}, and to a lesser extent 0\textsubscript{3}, N\textsubscript{2}0, CO, CH\textsubscript{4}, and 0\textsubscript{2} \cite{Miskolczi1993}). Holding vertical absorber content constant, variation in band-by-band TIR transmittance with path length is greatest at urban scales (approximately 1 to 50 \si{m}), where transparent spectral bands can quickly become opaque with small changes in path length or absorber content - illustrated in figure \ref{spectransheight}. Thus, transmittance of TIR near the surface is highly dependent on surface-sensor geometry, instrument spectral response, and atmospheric absorber content. Indeed, accurate assessment of atmospheric influence on TIR may be most complex when measured near the surface.

@@

\noindent where $ \sigma $ is the Stefan-Boltzmann constant and $ \overline{r} $ is Planck weighted mean broadband sensor response computed as,

@@

In addition, a simple approximation of $T_{bright}$ can be inferred from directional radiance using equation \ref{stefb1} by replacing $ L_z $ with $L'_z$ multiplied by a constant. This method is commonly used to infer T\textsubscript{bright} from infrared thermometers (IRT) operating over the atmospheric window, where atmospheric effects are minimal and T\textsubscript{bright} is a reasonably accurate approximation of T\textsubscript{surf}. However, constants must be calibrated for the range of expected T\textsubscript{surf} as the relationship between $ L_z $ and $L'_z$  is not perfectly linear with respect to emitter temperature.

Inversions of uncorrected $ L_z $ or $L'_z$ yield a temperature equal to that of a blackbody emitting the same amount of radiation as detected by the sensor. Since $ L_z $ ($L'_z$ ) is unlikely to be equal to $ L_0 $ ($L'_0$), T\textsubscript{bright} at $ z = 0 $ and T\textsubscript{bright} at $ z $ often show significant deviation based on sensor characteristics, ambient conditions, and surface-sensor geometry. Hence, remote sensed T\textsubscript{bright} is generally considered only a rough approximation representation of radiometric, kinetic, or thermodynamic T\textsubscript{surf}.

To retrieve a more accurate estimation of the 'true' T\textsubscript{surf}, the same inversions can be applied to TIR measurements after correction for atmospheric and surface emissivity effects (e.g. modification of the remote sensed TIR signal to represent that at $ z = 0 $ of a homogeneous blackbody emitter) to yield a direction radiometric surface temperature  T\textsubscript{rad} for atmospheric and emissivity corrected directional radiances, a hemispherical radiometric surface temperature T\textsubscript{hem} for atmospheric and emissivity corrected irradiances. T\textsubscript{rad} and T\textsubscript{hem} provide a better approximation of the ‘true’ T\textsubscript{surf} by representing the temperature at which the viewed surface is radiating, integrated over the sensor FOV.

@@

To calculate surface-sensor geometries, the Surface-Sensor-Sun Urban Model (SUM) \cite{Soux2004} is initialized with a simplified, orthogonal 3-dimensional DBM representing geometry of the area surrounding the sensor. SUM uses a four-dimensional array to represent surface morphology   with three spatial dimensions ($x$, $y$, and $z$), with $z$ representing height above the $x$, $y$ plane. An additional fourth dimension is used to store information describing each cell (in this case, distance from the point to the sensor). After specifying sensor position and FOV, the model determines which patches have an unobstructed line of sight to the sensor and calculates distance from "seen" patches to the sensor. Path lengths are binned at 5$^{\circ}$ increments of zenith angle and averaged to return an azimuthally-independent mean path length for each bin. In addition, while simulating path length geometries, SUM calculates view factors for each solid angle "slice", which are later used to weight 2-dimensional angular radiances in the hemispherical integration post-processing steps.

\begin{figure}[!ht]
	\includegraphics[width=\textwidth]{23radtran}
	\label{23radtran}
	\caption{A typical 2-dimensional (b) radiative transfer schematic adapted for an idealized 3-dimensional urban area (a). In 3-dimensions, path length for a given zenith angle can change significantly with azimuth angle. Dotted lines indicate absorption by the intervening atmospheric layer.}
\end{figure}

\subsection{Modeling hemispherical irradiances}
With path length geometries calculated in SUM, irradiances are modeled time-sequentially using version 4.1 of the MODerate resolution atmospheric TRANsmission radiative transfer code (MODTRAN) \cite{Berk1987}. At each time-step, T\textsubscript{bright} inferred from the measured irradiance and subtracted by a constant (6 \si{K} during nighttime runs and 4 \si{K} for daytime runs) is used to select a range of potential T\textsubscript{hem} which forms the bounds of the LUT for the target time-step. At-sensor spectral radiances for each path length are then modeled over a waveband of 0---2500 \si{cm^{-1}} at 0.5 \si{K} intervals over the LUT range. Atmospheric profiles are retrieved from 30-minute averages of T\textsubscript{air} and humidity, with aerosol and above-sensor conditions are informed by the mid-latitude summer standard atmosphere when daytime maximum T\textsubscript{air} is greater than 10 \si{\degreeCelsius} (the mid-latitude winter profile is substituted on days with maximum T\textsubscript{air} of less than 10 \si{\degreeCelsius}) \cite{Kantor1962}.

In this method, a "typical" longwave bandpass (approximately 4---42 \si{\micro\meter}) was extended to include much longer wavelengths. This was done for two reasons: 1. To accurately represent a longwave curve for typical urban T\textsubscript{surf}, which have significant emittance into wavelengths much longer than 42 \si{\micro\meter}. 2. To replicate the signal from a silicone-domed pyrgeometer, which is transmissive of radiation in wavelengths. A "typical" longwave bandpass underestimates a pyrgeometer signal by approximately 5---9 \si{\watt\per\square\meter}, depending on emitter temperature. Figure \ref{dometrans} comparison of ‘typical’ and ‘extended’ longwave bandpasses.

\begin{figure}[!ht]
	\includegraphics[width=\textwidth]{dometrans}
	\label{dometrans}
	\caption{ddddd}
\end{figure}

\section{Evaluation of the method using profiles of upwelling longwave radiation over a homogeneous planar surface}
